--- 
title:          "Python Bookdown"
author:         "Yong Keh Soon"
date:           "`r Sys.Date()`"
site:           bookdown::bookdown_site
output:         bookdown::bs4_book
url:            https://github.com/yongks/python_bookdown
github-repo:    yongks/python_bookdown
description:    This is a python cookbook, written using RMarkdown Notebook.
---

```{r, include=FALSE}
## This is always the FIRST file when building the book
set.seed(2020)

## Global environment  setting for entire book
## further look and feel setting, refer to file: _output.yml

library(knitr)
knitr::opts_chunk$set(echo=TRUE, 
                      message=FALSE, 
                      fig.width=2.6736, 
                      fig.height=2.5, 
                      fig.show='hold', 
                      error=TRUE, 
                      results='hold',
                      collapse=FALSE,
                      cache=TRUE) 
```


```{r include=FALSE}
library(reticulate)
use_condaenv('base')
```


# About This Book {-}

## Motivation {-}

This is a a python cookbook, serving as a quick reference to python and its popular library. The content covers python fundamentals, data manipulation, plotting, machine learning and sentiment analysis.

The main motivation of the book is for my personal reference. Therefore, it is written in a manner according to my thinking process. If you are like me who work on python as part-time basis, this book may help you refresh your memories quickly.

## Building The Book {-}

Although this book is written for python code, it is written using Bookdown tool (a R library). This is made possible with **reticulate** R library Python for R integration with Python. All content pages of the book are written as **RMarkdown** files, rendered by **Bookdown** in **BS4** (bootstrap 4, with 3 columns layout) output format.

The output of the renders goes into "/doc" folder. When uploaded to github, **/doc** folder will be served as Github Pages, which you are reading right now.

### Ingridients {-}

Here are the key ingredients used to build this book.

- [R Language](https://www.r-project.org/)
- [RMarkown](https://https://www.markdownguide.org/basic-syntax/)
- [Bookdown](https://bookdown.org/yihui/bookdown/get-started.html)
- [RStudio IDE](https://posit.co/downloads/)
- [Github Pages](https://docs.github.com/en/pages/quickstart)

### Environment {-}

The book is build on below Python environment:

- Anaconda with "base" environment
- Python 3.9.13
- pandas (1.4.4)
- numpy (1.23.4)
- scipy (1.9.3)
- scikit-learn (1.1.3)
- seaborn (0.12.1)
- matplotlib (3.6.2)
- plotnine (0.10.1)
- nltk (3.7)
- statsmodel (0.13.2)
- nlpia (0.5.2)
- bs4 (4.11.1)
